Model Comparison

### 2020-04-20 stats/model_comparison.Rmd
update supplement

@@

saveRDS(model_by_chain, "../saves/pred_model_likelihood_chain.rds")

@@

saveRDS(model, "../saves/pred_model_likelihood.rds")

@@

saveRDS(model_comp, "../saves/pred_model_comparison.rds")

@@

saveRDS(model_by_chain, "../saves/expl_model_likelihood_chain.rds")

@@

saveRDS(model, "../saves/expl_model_likelihood.rds")

@@

saveRDS(model_comp, "../saves/expl_model_comparison.rds")

>>>>

# Model predictions

Model predictions can be downloaded via the following link: https://keeper.mpdl.mpg.de/d/7ae3805dba064bada8e5/
In the code below, model predictions are assumed to be in a subfolder called `saves/`.

@@

#saveRDS(model_by_chain, "../saves/pred_model_likelihood_chain.rds")

@@

#saveRDS(model, "../saves/pred_model_likelihood.rds")

@@

#saveRDS(model_comp, "../saves/pred_model_comparison.rds")

@@

#saveRDS(model_by_chain, "../saves/expl_model_likelihood_chain.rds")

@@

#saveRDS(model, "../saves/expl_model_likelihood.rds")

@@

#saveRDS(model_comp, "../saves/expl_model_comparison.rds")
